Summary of the Iberian Bees Database

### 2022-03-14 Manuscript/Summary/Summary.Rmd

master <- read.csv("../../Data/Processing_iberian_bees_raw/Iberian_species_masterlist.csv", stringsAsFactors = FALSE)
master$accepted_name <- paste(master$Genus, master$Species, sep = " ")
colnames(data)
colnames(master)
data[which(!data$accepted_name %in% master$accepted_name), ] # OK
master[which(!master$accepted_name %in% data$accepted_name), ]
# we are missing ~100 species, mostly parasites!
length(unique(data$accepted_name))
nrow(master)
```

The Iberian Bee Database contains **`r nrow(data)` entries** of bee occurrences over the peninsula and nearby islands. We have at least one record of **`r length(unique(data$accepted_name))` species** out of the **`r nrow(master)` species** known to occur in the Iberian Peninsula.

@@

```{r echo=FALSE, fig.align='center', out.width="70%"}
# Prepare top 20 records
top_20 <- data %>%
  filter(!accepted_name == "Apis mellifera") %>%
  group_by(accepted_name) %>%
  summarise(no_rows = length(accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$accepted_name <- factor(top_20$accepted_name, levels = top_20$accepted_name)
# Plot
ggplot(top_20, aes(x = accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, face = "italic")) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```

@@

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Prepare top 20 records
by_year <- data %>% filter(!accepted_name == "Apis mellifera")

>>>>

master <- read.csv("../../Data/Processing_iberian_bees_raw/Iberian_species_masterlist.csv", stringsAsFactors = FALSE)
master$Accepted_name <- paste(master$Genus, master$Species, sep = " ")
colnames(data)
colnames(master)
data[which(!data$Accepted_name %in% master$Accepted_name), ] # OK
master[which(!master$Accepted_name %in% data$Accepted_name), ]
# we are missing ~100 species, mostly parasites!
length(unique(data$Accepted_name))
nrow(master)
```

The Iberian Bee Database contains **`r nrow(data)` entries** of bee occurrences over the peninsula and nearby islands. We have at least one record of **`r length(unique(data$Accepted_name))` species** out of the **`r nrow(master)` species** known to occur in the Iberian Peninsula.

@@

```{r echo=FALSE, fig.align='center', out.width="70%"}
# Prepare top 20 records
top_20 <- data %>%
  filter(!Accepted_name == "Apis mellifera") %>%
  group_by(Accepted_name) %>%
  summarise(no_rows = length(Accepted_name)) %>%
  arrange(-no_rows) %>%
  slice(1:20)
# Fix row position
top_20$Accepted_name <- factor(top_20$Accepted_name, levels = top_20$Accepted_name)
# Plot
ggplot(top_20, aes(x = Accepted_name, y = no_rows)) +
  geom_bar(stat = "identity", fill = "#287D8EFF") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8, face = "italic")) +
  ylab("Number of records") +
  xlab("Species") +
  scale_y_continuous(expand = c(0, 0))
```

@@

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Prepare top 20 records
by_year <- data %>% filter(!Accepted_name == "Apis mellifera")
